Prediction of Power Generation

### 2020-08-05 LaTeX_Code/Reports/old_reports/abstract_Berlin.tex
Updated main files

\documentclass[12pt]{article}
\usepackage[table]{xcolor}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage[english]{babel}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{blkarray}
\usepackage{float}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{siunitx}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{proposition}
\newtheorem{exmp}{Example}[section]\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}
\newtheorem{ex}{Exercise}
\theoremstyle{definition}
\theoremstyle{remark}
\bibliographystyle{elsarticle-num}

\DeclareMathOperator{\sinc}{sinc}
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\matindex}[1]{\mbox{\scriptsize#1}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\prob}{\mathbb{P}}

\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}

\title{Uncertainty Quantification in Wind Power Forecasting  \\ Conference Abstract}

@@

%\pagebreak
%\tableofcontents
%\pagebreak
\section{Abstract 600 char}
Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest. We propose a model to simulate and quantify uncertainties in such forecasts. This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function. The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We apply the model to historical Uruguayan data and forecasts.

@@

The adoption of renewable energy is accelerating due to technological advancements. However, the power generated by renewables is difficult to predict and thus such predictions require advanced uncertainty quantification techniques to ensure the bare minimum of meeting electricity power demands. This is also of importance for energy trading and insurance, that it is to deliver power in an optimal cost-effective way to adhere to a variety of financial contracts. Uncertainty quantification is key in the design of financial contracts and taking investment decisions in the energy sector. Additionally, it assists in the placement and design of renewable power plants.

@@

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[activeacute, english]{babel}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{subcaption}

\newcommand\dist{\stackrel{\mathclap{\footnotesize\mbox{d.}}}{=}}
\usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
\usepackage[spanish,onelanguage]{algorithm2e}
\newtheorem{theorem}{Teorema}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposición}
%\newenvironment{proof}[1][Demostración]{\begin{trivlist}
%		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definición]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Ejemplo]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Nota]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\negr}[1]{\textit{\textbf{#1}}}

\title{On the Uncertainty of Wind Power Forecasts \\ Abstract}

@@

@@

The adoption of renewable energy is accelerating due to technological advancements. However, the power generated by renewables is difficult to predict and thus such predictions require advanced uncertainty quantification techniques to ensure the bare minimum of meeting electricity power demands. This is also of importance for energy trading and insurance, that it is to deliver power in an optimal cost-effective way to adhere to a variety of financial contracts. Uncertainty quantification is key in the design  financial contracts and taking investment decisions in the energy sector. Additionally, it assists in the placement and design of renewable power plants.

@@

%\subsection{Model}
%\begin{thebibliography}{99}
%	\bibitem{apo} Apostol, T. (1974). \emph{Mathematical Analysis} (2nd ed.),  Addison-Wesley. pp.218-230
%	\bibitem{E} Cabaña, E. (2012). \emph{Introducción a los
%		procesos estocásticos}, Notas
%	para el Curso de la Licenciatura en Estadística, Universidad de la República. pp.98-115
%\end{thebibliography}

### 2020-08-05 LaTeX_Code/Reports/old_reports/abstract_Berlin_NT.tex
Updated main files

\title{Uncertainty Quantification in Wind Power Forecasting  \\ Conference Abstract}

\author{Waleed Alhaddad \quad  Ra\'ul Fidel Tempone \\ CEMSE, KAUST}

@@

%\pagebreak
%\tableofcontents
%\pagebreak
\section{Abstract 600 char}
Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest. We propose a model to simulate and quantify uncertainties in such forecasts. This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function. The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We apply the model to historical Uruguayan data and forecasts.

@@

    We are able to simulate and quantify uncertainties in a variety of wind power generation forecasts while taking into account the skewness of the errors. This method is non-intrusive and is independent of forecasting technology or future developments. Through optimization, we update and tune the parameters of our SDE as we receive new sets of observations and their associated forecasts. Additionally, we are able to compare in a quantitative manner the different forecast technologies and how they behave in different real-world scenarios. This model is to be extended to the uncertainty quantification of other power generation sources such as the uncertainties in the power generation of solar power plants. This introduces new challenges in terms of optimization and modeling. Finally, we apply our model to synthetic and real wind power generation data for benchmarking. We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.

@@

\section{Conclusion}
We were able to simulate and quantify the uncertainties for a diverse range of forecasts based on the Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016. We compare our results to similar works in the literature. And we highlight the importance of asymmetry and the avoidance of phase shift artifacts which we were able to overcome.

>>>>

\title{Uncertainty Quantification in Wind Power Forecasting  \\ }

\author{Waleed Alhaddad }

@@

%\pagebreak
%\tableofcontents
%\pagebreak
\section{Abstract}
Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest. We propose a model to simulate and quantify uncertainties in such forecasts. This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function. The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We will apply the model to historical  data and forecasts.

@@

    We are able to simulate and quantify uncertainties in a variety of wind power generation forecasts while taking into account the skewness of the errors. This method is non-intrusive and is independent of forecasting technology or future developments. Through optimization, we update and tune the parameters of our SDE as we receive new sets of observations and their associated forecasts. Additionally, we are able to compare in a quantitative manner the different forecast technologies and how they behave in different real-world scenarios. This model is to be extended to the uncertainty quantification of other power generation sources such as the uncertainties in the power generation of solar power plants. This introduces new challenges in terms of optimization and modeling. Finally, we apply our model to synthetic and real wind power generation data for benchmarking. We apply the model to real  wind power production data and their corresponding numerical forecasts.

@@

\section{Conclusion}
We  propose a model to quantify the uncertainties in wind power generation forecasts. It is important to note that this approach is agnostic of forecasting technology. We have also taken into account the physical limits of the model by respecting the full installation power of the wind farm. Additionally, we have taken into account skew-symmetric errors. The skewness of the forecast errors is necessary to correctly model the errors when operating near full installation power production or in cases of extremely low wind power production.

### 2020-08-05 LaTeX_Code/Reports/old_reports/continous_report.tex
Updated main files

List of changes in this iteration:
\begin{itemize}
\item Implemented Beta transitions
\item Implemented time dependent forecast
\item Numerically solve for the first two moments
\item Time dependent path variability parameter
\item Convergence results of all the above
\end{itemize}

Next steps:
\begin{itemize}
\item Use real data and forecast.
\item Try exponential decay in the mean reversion.
\end{itemize}

@@

\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent  parameters }
We approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
\begin{equation}
\ell(\bm{\theta}; V)= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log(\frac{V_{j,i+1}+1}{2}) + (\beta -1) \log(1-\frac{V_{j,i+1}+1}{2}) - \log ( 2 B(\alpha, \beta))
\end{equation}

@@

\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameters }
We generate samples using the previous Euler scheme to numerically compute the moments before each realization.We obtain the following sample paths
\begin{figure}
    \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0503.pdf}
        \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0505.pdf}

@@

\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameter }
We perform a convergence test for speed of reversion parameter $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$. We obtain the following convergence result
\begin{figure}
    \includegraphics[scale=0.4]{Figures/conv_M_beta_flex_10.pdf}
    \includegraphics[scale=0.4]{Figures/conv_N_beta_flex_35.pdf}
  \caption{ Convergence results for Beta transitions with $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$   }
  %\label{fig:boat1}
\end{figure}

>>>>

List of changes in this iteration:
\begin{itemize}
\item Matched data with every forecast
\item Normalized according to installed power of each period
\item Interpolated the forecast using cubic splines.

\end{itemize}

Next steps:
\begin{itemize}
\item upgrade the numerical integrator and use the interpolated forecast
\item Check performace using the interpolated forecasts and data
\end{itemize}

@@

\begin{frame}\frametitle{ Case 5.2.1: Time dependent Forecast  }
We approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
\begin{equation}
\ell(\bm{\theta}; V)= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log(\frac{V_{j,i+1}+1}{2}) + (\beta -1) \log(1-\frac{V_{j,i+1}+1}{2}) - \log ( 2 B(\alpha, \beta))
\end{equation}

@@

\begin{frame}\frametitle{ Case 5.2.1: Time dependent Forecast  }
We generate samples using the previous Euler scheme to numerically compute the moments before each realization.We obtain the following sample paths
\begin{figure}
    \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0503.pdf}
        \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0505.pdf}

@@

\begin{frame}\frametitle{ Case 5.2.1: Time dependent Forecast  }
We perform a convergence test for speed of reversion parameter $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$. We obtain the following convergence result
\begin{figure}
    \includegraphics[scale=0.4]{Figures/conv_M_beta_flex_10.pdf}
    \includegraphics[scale=0.4]{Figures/conv_N_beta_flex_35.pdf}
  \caption{ Convergence results for Beta transitions with $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$   }
  %\label{fig:boat1}
\end{figure}

\begin{frame}\frametitle{ Real data and Forecast  }
\begin{itemize}
\item We have compiled 1265 forecasts from two full years (2016-2017) along with the measured real power generation.
\item The real power generation data has been matched to the forecast using timestamps (Unix time). 
We have 72 hourly observations for each forecast.
\item Data is normalized according to the installed power at that specific period of the forecast.
\end{itemize}

\begin{frame}\frametitle{  Real data and Forecast }
\begin{figure}
    \includegraphics[scale=0.3]{Figures/forecast_data.eps}
  \caption{ Random selection of forecasts and their associated real power generation data }
  %\label{fig:boat1}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ Forecast cubic splines interpolation }

For better numerical integration of the ODEs in order to find the moments of the stochastic process $V_t$, we need to interpolate between the discrete values of the forecast (as the given forecast is not fine-grained). \\

In this case, we choose to use cubic splines.

\begin{frame}\frametitle{ Forecast cubic splines interpolation }

\begin{figure}
    \includegraphics[scale=0.3]{Figures/forecast_splines.eps}
  \caption{  Random selection of forecasts discrete values and the associated cubic splines interpolation }
  %\label{fig:boat1}
\end{figure}
